Comparative Analysis of the wav2vec 2.0 Feature Extractor

### 2023-03-05 tables/features_pretraining.tex
tables: WERs for all subsets template

\centering
\caption{Effect of pre-training the wav2vec 2.0 feature extractor using the unsupervised loss on the same data (Librispeech 960h).}
\label{table:features_pretraining}
\begin{tabular}{|c|c|S|}
\hline
\multicolumn{2}{|c|}{Feature Extractor} &       {WER} \\\hline
                              Trainable & Pretrained & {dev-other} \\\hline\hline
                                    yes &         no &         6.8 \\\cline{2-3}
                                        &        yes &         6.9 \\\cline{1-1}\cline{3-3}
                                     no &            &         7.1 \\
\hline
\end{tabular}

>>>>

\centering
\caption{Effect of pre-training the wav2vec 2.0 feature extractor using the unsupervised loss on the same data (Librispeech 960h).}
\label{table:features_pretraining}
\begin{tabular}{|c|c|S|c|S|c|}
\hline
\multicolumn{2}{|c|}{Feature Extractor} & \multicolumn{4}{c|}{{WER}} \\\cline{3-6}
                 \multicolumn{2}{|c|}{} & \multicolumn{2}{c|}{{dev}} & \multicolumn{2}{c|}{{test}} \\\hline
                              Trainable & Pretrained &                    {clean} & other &                     {clean} & other \\\hline\hline
                                    yes &         no &                            &   6.8 &                             &       \\\cline{2-6}
                                        &        yes &                            &   6.9 &                             &       \\\cline{1-1}\cline{3-6}
                                     no &            &                            &   7.1 &                             &       \\
\hline
\end{tabular}
